\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{epsfig}
\usepackage[tight]{subfigure}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=red,
}

\newcommand{\myhw}[5]{
  \pagestyle{myheadings}
  \thispagestyle{plain}
%   \newpage
   \setcounter{page}{1}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to \textwidth { {\bf {\small CMSC 498L}:~Introduction to Deep Learning \hfill {\small #2}} }
       \vspace{6mm}
       \hbox to \textwidth { {\Large \hfill #1  \hfill} }
       \vspace{4mm}
      \hbox to \textwidth { {\it Instructor: {\rm #3} \hfill TA: {\rm #4} } }
      \vspace{2mm}}
      
    }
   \end{center}
   
    \pagestyle{fancy}
    \fancyhf{}
    \lhead{{\small CMSC 498L}:~Intro to Deep Learning}
    \rhead{Assignment 1}
    \cfoot{--- \thepage~---}
    \vspace*{4mm}
}

\parindent 0in
%\parskip 1.5ex
% \renewcommand{\baselinestretch}{1.25}

\begin{document}

\myhw{Assignment 1}{Released: Feb-14. Due Feb-21.}{Abhinav Shrivastava}{Pulkit Kumar}

\section{Probability}
	
\begin{enumerate}
  \item \textbf{Density function}. Let $p$ be a Gaussian distribution with zero mean and variance of 0.1. Compute the density of $p$ at 0.
  
  \item \textbf{Conditional probability}. A student is taking a one-hour-time-limit makeup examination. Suppose the probability that the student will finish the exam in less than x hours is $x/2$, $\forall \text{x}\in[0,1]$. 
  %for all $0 \leq x \leq 1$. 
  Given that the student is still working after 0.75 hour, what is the conditional probability that the full hour will be used?
  
  \item \textbf{Bayes rule}. Consider the probability distribution of you getting sick given the weather in the table below.
  
  \vspace{1mm}
  \begin{tabular}{@{}ccccc@{}}
  \toprule
  \multirow{2}{*}{Sick?} & \multicolumn{4}{@{}c@{}}{Weather}  \\
  \cmidrule{2-5}
      & sunny & rainy & cloudy & snow \\
  \midrule
  yes  & 0.144 & 0.02 & 0.016 & 0.02\\
  no & 0.576 & 0.08 & 0.064 & 0.08 \\
  \bottomrule
  \end{tabular}
  \vspace{1mm}
  
  Compute P$\left(\, \text{sick}=\text{yes}\mid\text{Weather}=\text{rainy} \,\right)$.
\end{enumerate}

\section{Calculus and Linear Algebra}

 For each of the following questions, we expect to see all the steps for reaching the solution.
	
\begin{enumerate}
\item Compute the derivative of the function $f(z)$ with respect to z $\left(\text{i.e., }\frac{df}{dz}\right)$, where $$f(z) = \frac{1}{1+e^{-z}}$$

\item Compute the derivative of the function $f(w)$ with respect to $w_i$, where $w, x \in \mathbb{R}^\text{D}$ and $$f(w) = \frac{1}{1+e^{-w^Tx}}$$

\item Compute the derivative of the loss function $J(w)$ with respect to $w$, where 
$$ J(w) = \frac{1}{2}\sum_{i=1}^{m} \left|w^{T}x^{(i)} - y^{(i)}\right| $$

\item Compute the derivative of the loss function $J(w)$ with respect to $w$, where 
$$ J(w) = \frac{1}{2}\left[ \sum_{i=1}^{m} \left(w^{T}x^{(i)} - y^{(i)}\right)^2 \right] + \lambda \|w\|^2_2 $$ 

\item Compute the derivative of the loss function $J(w)$ with respect to $w$, where 
$$ J(w) = \sum_{i=1}^{m} \left[y^{(i)} \log \left(\frac{1}{1 + e^{-w^{T}x^{(i)}}}\right) + \left(1 - y^{(i)}\right) \log \left(1- \frac{1}{1 + e^{-w^{T}x^{(i)}}}\right)\right] $$

\item Compute $\nabla_wf$, where $f(w) = \tanh \left[w^Tx\right]$.
	   
\item Find the solution to the system of linear equations given by Ax=b, where 
$$A = \left(\begin{array}{rrr} 2 & 1 & -1\\ -3 & -1 & 2 \\ -2 & 1 & 2 \end{array}\right) \quad \text{and} \quad b = \left(\begin{array}{r} 8 \\ -11 \\ -3 \end{array}\right).$$

\item Find the eigenvalues and associated eigenvectors of the matrix:

$$A = \left[\begin{array}{rrr} 7 & 0 & -3\\ -9 & -2 & 3 \\ 18 & 0 & -8 \end{array}\right] \quad $$


\end{enumerate}


\section{Activation functions}
For each of the following activation functions, write their equations and their derivatives. Plot the functions and derivatives, with $x\in \left[-5, 5\right]$ and $y\in\left[-10,10\right]$ plot limits. (No need to submit the code for plots.)

\begin{enumerate}
    \item Relu
    \item Tanh
    \item Softmax
    \item Sigmoid
    \item Leaky ReLU
    \item ELU (plot with $\alpha=0.3$)
    \item Sinc
\end{enumerate}

\vspace{20pt}

\paragraph{Notes:}
\begin{itemize}
    \item Submit the assignment on ELMS.
    \item Assignments have to be formatted in \LaTeX. You can use \href{https://www.overleaf.com/}{overleaf} for writing your assignments.
    \item Submit only the compiled PDF version of the assignment.
    \item Refer to \href{http://www.cs.umd.edu/class/spring2020/cmsc498L/#policy}{policies} (collaboration, late days, etc.) on the course website.
\end{itemize}

\end{document}